\documentclass[9pt]{developercv}

\begin{document}

\begin{minipage}[t]{0.41\textwidth}
  \vspace{-\baselineskip}

  \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Petr}}}}}
  \\
  \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Penicka}}}}}

  \vspace{6pt}

  {\huge Senior Frontend Engineer}
\end{minipage}
\begin{minipage}[t]{0.275\textwidth}
  \vspace{-\baselineskip}

  \icon{MapMarker}{12}{Prague, Czech Republic}\\
  \icon{At}{12}{\href{mailto:petr.penicka@gmail.com}{petr.penicka@gmail.com}}\\
  \icon{Globe}{12}{\href{https://ppenicka.me}{ppenicka.me}}\\
  % \icon{Phone}{12}{+66 098 1152 498}\\
\end{minipage}
\begin{minipage}[t]{0.34\textwidth}
  \vspace{-\baselineskip}

  \icon{Linkedin}{12}{\href{https://github.com/ppenicka}{linkedin.com/in/petr-penicka}}\\
  \icon{Github}{12}{\href{https://github.com/ppenicka}{github.com/ppenicka}}\\

\end{minipage}

\vspace{0.1cm}

\cvsect{About Me}

\begin{minipage}[t]{1\textwidth}
  \vspace{-\baselineskip}

  {Senior Frontend Engineer specializing in JavaScript technologies, mainly Vue.js, Nuxt.js, React, Next.js and TypeScript. Before switching to software engineering, I gained 12+ years of experience in the tech industry as a Program Manager and a Technical Writer. This makes me stand out among other engineers due to strong communication, planning, and organizational skills. If you’re seeking an engineer who not only delivers high-quality code but also collaborates seamlessly with colleagues in non-technical roles, I believe I would be an excellent fit for your team.}\\
\end{minipage}

\cvsect{Experience}

\begin{entrylist}
  \entry
  {2024 --  present}
  {Senior Frontend Engineer}
  {Slash.Digital, Munich, Germany}
  {Developing high-exposure web applications and websites that support clients' marketing campaigns and have significant impact on the growth of their business.\\ \texttt{Vue.js}\slashsep\texttt{Nuxt.js}\slashsep\texttt{TypeScript}\slashsep\texttt{Tailwind}\slashsep\texttt{SCSS}\slashsep\texttt{SWRV}\slashsep\texttt{Wagtail CMS}}
  \entry
  {2021 --  2024}
  {Frontend Engineer}
  {Glovo, Barcelona, Spain}
  {Developed UIs for billing, invoicing, payment gateway configuration, security features (CAPTCHA, 2FA, phone verification), and partner payout settings. Led the migration of the courier registration site from WordPress to a Nuxt.js and Prismic-based custom solution. Contributed to web app modularization and monorepo migration.\\ \texttt{Vue.js}\slashsep\texttt{Vuex}\slashsep\texttt{Vue Testing Library}\slashsep\texttt{Pinia}\slashsep\texttt{Nuxt.js}\slashsep\texttt{Prismic}\slashsep\texttt{TypeScript}\slashsep\texttt{Sass}\slashsep\texttt{Tailwind}\slashsep\texttt{Element UI}\slashsep\texttt{Prismic CMS}}
  \entry
  {2022 --  2023}
  {Instructor}
  {Codeworks, Barcelona, Spain}
  {As a part-time gig during my main job at Glovo, I was tutoring at weekend classes of Codeworks, Barcelona’s top rated software engineering bootcamp.\\ \texttt{JavaScript}\slashsep\texttt{TypeScript}\slashsep\texttt{React}\slashsep\texttt{Express}\slashsep\texttt{Node.js}}
  \entry
  {2020 -- 2021}
  {Frontend Developer}
  {ManoMano, Barcelona, Spain}
  {Implemented redesign of the main product page (1M+ daily views) and navigation menu, customized UI for professional users, and migrated the codebase to TypeScript.\\ \texttt{React}\slashsep\texttt{Redux}\slashsep\texttt{Next.js}\slashsep\texttt{Sass}\slashsep\texttt{Enzyme}\slashsep\texttt{Jest}\slashsep\texttt{TypeScript}}
  \entry
  {2016 -- 2019}
  {Program Manager}
  {Red Hat, Brno, Czech Republic}
  {Managed the planning, development and delivery of 20+ releases of various Red Hat products. }
  \entry
  {2015}
  {Documentation Program Manager}
  {Red Hat, Brno, Czech Republic}
  {Managed a team of technical writers responsible for documentation of various Red Hat products. }
  \entry
  {2012 -- 2014}
  {Technical Writer}
  {Red Hat, Brno, Czech Republic}
  {Authored and maintained documentation of Red Hat products. }
  \entry
  {2008 -- 2012}
  {Technical Writer}
  {Kentico Software, Brno, Czech Republic}
  {Authored and maintained product documentation of Kentico CMS. }
\end{entrylist}

\cvsect{Education}

\begin{entrylist}
  \entry
  {2020}
  {Software Engineering}
  {Codeworks, Barcelona, Spain}
  {Immersive software engineering bootcamp focused on full-stack web development.}
  \entry
  {2013}
  {Master's Degree in Applied Informatics}
  {Masaryk University, Brno, Czech Republic}
  {Study field Service Science, Management and Engineering.}
  \entry
  {2011}
  {Bachelor's Degree  in Applied Informatics}
  {Masaryk University, Brno, Czech Republic}
  {Study field Applied Informatics.}
\end{entrylist}


\begin{minipage}[t]{1\textwidth}
  \vspace{-\baselineskip}

  \cvsect{Languages}

  \textbf{English} - proficient (C2)\hfill\slashsep\hfill
  \textbf{Spanish} - intermediate (B1)\hfill\slashsep\hfill
  \textbf{German} - intermediate (B1)\hfill\slashsep\hfill
  \textbf{Czech} - native (C2)
% \end{minipage}
% \begin{minipage}[t]{0.55\textwidth}
%   \vspace{-\baselineskip}

%   \cvsect{Current Career Goal}

%   Expand my client base so that I can utilize my full time capacity on interesting and technically challenging projects, in order to further establish myself as a recognized freelancer while maintaining stable growth of technical skills and expertise.
\end{minipage}
% \hfill

\end{document}
